Instructions for developing new pages for the MarineOmics webpage

### 2023-08-27 ADMIN_01_submissions_instructions.Rmd
added policy for creatign a page and what to do when conflictsarise

If you are interested in submitting new content to the
MarineOmics.github.io website, this is the guide for you! While the
website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content.
Below we provide general instructions as well as examples of how to
build specific features (eg., tables, code chunks). Prior to developing
new pages, please contact the current Website Manager Jason Johns
(jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other
questions, comments, or features you'd like added to this guide.

@@

@@

*Note: it's a good idea to look at existing .Rmd scripts (including [the
one that codes for this
page](https://github.com/MarineOmics/marineomics.github.io/blob/main/submissions_instructions.Rmd))
to see examples of how a particular feature can be accomplished, such as
citing references, linking a website, building a table, incorporating
figures, etc. We will explicitly go over some of those features below,
but there are many other bells and whistles that can be explored through
online resources.*

@@

>>>>

If you are interested in submitting new content to the
MarineOmics.github.io website, this is the guide for you! While the
website managers will work with you to help prepare and publish your new
page, this guide can be a useful resource as you develop your content.
Below we provide general instructions as well as examples of how to
build specific features (eg., tables, code chunks). Prior to developing
new pages, please first contact the current Website Manager Jason Johns
(jasonjohns[at]ucsb.edu). Do not hesitate to reach out with any other
questions, comments, or features you'd like added to this guide.

@@

### MarineOmics publishing process
#### Content development and review process
1. Initiation: The potential contributor contacts the website manager via email or the discussion forum with an idea.
<br>
2. Development: Meet with the website manager, Katherine Silliman and/or Sam Bogan (Working Group Co-leaders) <br>
    + All active members will be notified and invited to be involved in the review process. <br>
    + The contributor presents their idea for new material. <br>
    + There will be regular meetings (frequency decided by those involved) with the website manager, Katherine Silliman and/or Sam Bogan, and any other participating members for progress updates and support. <br>
3. Review: Full drafts of content will be reviewed by the website manager, Katherine Silliman and/or Sam Bogan, and at least one other active MarineOmics member assigned to the project.

*See the [bottom of the page](#conflicts) for our policy on disagreements or conflicts during the development process

@@

*Note: it's a good idea to look at existing .Rmd scripts (including [the
one that codes for this
page](https://github.com/MarineOmics/marineomics.github.io/blob/main/ADMIN_01_submissions_instructions.Rmd))
to see examples of how a particular feature can be accomplished, such as
citing references, linking a website, building a table, incorporating
figures, etc. We will explicitly go over some of those features below,
but there are many other bells and whistles that can be explored through
online resources.*

@@

<a id="conflicts"></a>

#### Content/wording conflicts
At any point in the process, disagreements on what content to include may arise. These include but are not limited to: recommendations for experimental design, techniques, and phrasing. All disagreements will be approached with the same method(s).
<br>
<br>
Disagreements will be discussed with all of those involved at the time that the disagreement arises. The first attempt at resolving the disagreement will be via discussion. If a resolution is not agreed upon by all parties through discussion, it will be put to a majority vote including all of those actively involved at the time, not including the content author. In case of a tie, a MarineOmics senior scientist will be assigned to break the tie.
